Wrangling multivariate spatio-temporal data with the R package cubble

### 2022-04-29 5-conclusion.Rmd
add highlight of examples in conclusion

>>>>

The data structure and software are demonstrated with extensive examples. These include creating and coercing wild-caught data with potential mismatch on sites, handling hierarchical data, matching series spatially and temporally, reproducing ERA5 results from NetCDF data, and, lastly fitting into the interactive graphic pipeline of \pkg{plotly} and \pkg{leaflet}.

### 2022-04-29 arxiv/cubble-arxiv.tex
add highlight of examples in conclusion

{\centering \includegraphics[width=0.5\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/cube-def}

@@

\caption{An illustration of the conceptualised spatio-temporal cube with three axes: time, site, and variable.}\label{fig:cube-def}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/diagram-keynotes/diagram-keynotes.007}

@@

\caption{An illustration of the conceptual spatio-temporal cube with different slicing on time, site, and variable. For each axis, the slicing can be on a single value or a set of values.}\label{fig:cube-def}
\end{figure}
